Secondary analysis of tables

### 2019-10-16 Analysis/06_Analysis_Tables.Rmd
Adjust to include modularity

```{r}
# Selected data for correlation
# Remove small/large networks
mtx0_cor <- mtx0[ mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, min, na.rm = TRUE) > min_genes &
                  mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, max, na.rm = TRUE) < max_genes, ]
# Remove size columns
mtx0_cor <- mtx0_cor %>% dplyr::select(contains("Coherence"), contains("Number"), contains("P-value"))
# Jitter STRING p-value a bit
set.seed(1)
mtx0_cor$`String P-value` <- jitter(mtx0_cor$`String P-value`, amount = 0.0001)
# Actual correlation
diff_cors <- cor(mtx0_cor, use = "pairwise.complete.obs")
# Average correlation with network size
print(paste0("Average correlation with network size: ", mean(diff_cors[grepl("Number", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))])))
# Average correlation of coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)) & grepl("String", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors)) & grepl("String", colnames(diff_cors))]
print(paste0("Average correlation of STRING coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation of coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("P-value", colnames(diff_cors))]
print(paste0("Average correlation of coherences and p-value: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))

@@

  mtx_traits_selected_to_plot <- data.frame(Disease = rownames(mtx_traits_selected), 
                                            Pvalue = mtx_traits_selected[, grepl(paste0(databases, " P-value"), colnames(mtx_traits_selected)) ], 
                                            Coherence = mtx_traits_selected[, grepl(paste0(databases, " Coherence"), colnames(mtx_traits_selected)) ])
  # Remove noninformative rows
  mtx_traits_selected_to_plot <- mtx_traits_selected_to_plot[!is.na(mtx_traits_selected_to_plot$Coherence), ]
  # Sort by decreasing level of coherence
  mtx_traits_selected_to_plot$Disease <- factor(mtx_traits_selected_to_plot$Disease, levels = mtx_traits_selected_to_plot$Disease[order(mtx_traits_selected_to_plot$Coherence)])

>>>>

```{r}
# Selected data for correlation
# Remove small/large networks
mtx0_cor <- mtx0[ mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, min, na.rm = TRUE) > min_genes &
                  mtx0 %>% dplyr::select(starts_with("Size")) %>% apply(., 1, max, na.rm = TRUE) < max_genes, ]
# Remove size columns
mtx0_cor <- mtx0_cor %>% dplyr::select(contains("Coherence"), contains("Number"), contains("P value"), contains("Modularity"))
# Jitter STRING p-value a bit
set.seed(1)
mtx0_cor$`String P value` <- jitter(mtx0_cor$`String P value`, amount = 0.0001)
# Actual correlation
diff_cors <- cor(mtx0_cor, use = "pairwise.complete.obs")
# Average correlation with network size
diff_cors_selected <- diff_cors[grepl("Number", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation with network size: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of STRING and STRING filtered coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)) & grepl("String", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors)) & grepl("String", colnames(diff_cors))]
print(paste0("Average correlation of STRING coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of coherences
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("Coherence", colnames(diff_cors))]
print(paste0("Average correlation of coherences: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))
# Average correlation of coherences and p-value
diff_cors_selected <- diff_cors[grepl("Coherence", rownames(diff_cors)), grepl("P value", colnames(diff_cors))]
print(paste0("Average correlation of coherences and p-value: ", mean(diff_cors_selected[upper.tri(diff_cors_selected)])))

@@

  mtx_traits_selected_to_plot <- data.frame(Disease = rownames(mtx_traits_selected), 
                                            Pvalue = mtx_traits_selected[, grepl(paste0(databases, " P value"), colnames(mtx_traits_selected)) ], 
                                            Coherence = mtx_traits_selected[, grepl(paste0(databases, " Coherence"), colnames(mtx_traits_selected)) ])
  # Remove noninformative rows
  mtx_traits_selected_to_plot <- mtx_traits_selected_to_plot[!is.na(mtx_traits_selected_to_plot$Coherence), ]
  # Sort by decreasing level of coherence
  mtx_traits_selected_to_plot$Disease <- factor(mtx_traits_selected_to_plot$Disease, levels = mtx_traits_selected_to_plot$Disease[order(mtx_traits_selected_to_plot$Coherence)])
